Manuscript for a Data Analysis Project: Diabetes Diagnosis

### 2024-07-13 code/analysis-code/statistical_analysis_code.qmd
Finished Part 4
Completed the modeling and updated the manuscript, currently working on references

```{r}
# Loading in necessary libraries
library(ISLR2)
library(MASS)
library(boot)
library(glmnet)
library(ggplot2) 
library(pls)
library(leaps)
library(gam)
library(fastDummies)
library(caret)
library(nnet)
library(MLmetrics)
library(randomForest)
```

@@

|------------------|------------------------------------------------------|

@@

```{r}

@@

```{r}

>>>>

```{r}
# Loading in necessary libraries
library(ISLR2)
library(MASS)
library(boot)
library(glmnet)
library(ggplot2) 
library(pls)
library(leaps)
library(gam)
library(fastDummies)
library(caret)
library(nnet)
library(MLmetrics)
library(randomForest)
library(here) #to set paths
```

@@

|------------|------------------------------------------------------------|

@@

```{r}
set.seed(12345)
knn_model <- train(Diabetes_012 ~ ., 
                   data = sample_data, 
                   method = "knn", 
                   trControl = train_control,
                   preProcess = c("center", "scale"),
                   metric = "Accuracy") 
```

@@

```{r}
# Make predictions on the same data (or a test dataset if you have one)
predictions <- predict(knn_model, newdata = sample_data)

Plot of accuracy

```{r}
accuracy <- data.frame(
  Model = c("Logistic Regression", "Random Forest", "KNN"),
  Accuracy = c(
    max(logistic_model$results$Accuracy),
    max(rf_model$results$Accuracy),
    max(knn_model$results$Accuracy)
  )
)

accuracy_plot <- ggplot(accuracy, aes(x = Model, y = Accuracy, fill = Model)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Model Accuracy Comparison", y = "Accuracy", x = "Model") +
  scale_fill_brewer(palette = "Set2")
```

```{r}
# Define the file path to save the plot
figure_file <- here("results", "figures")

ggsave(filename = "model_accuracy_comparison.png", plot = accuracy_plot, path = figure_file)
```

### 2024-07-13 products/manuscript/Manuscript.qmd
Finished Part 4
Completed the modeling and updated the manuscript, currently working on references

|------------------|------------------------------------------------------|

@@

*\*Analysis methods will be included in later part of project*

@@

### Explain the question to be answered using the data

### What will be your outcome(s) of interest (if any)?

@@

For my analysis, I will first look at the distributions of each variable to identify if the dataset is balanced and outliers. I do not think any data cleaning will need to be done as that was completed when the data was collected from the CDCs website. Next, I will create a correlation matrix to view the correlations between each predictor and the response variable. After viewing the correlations, I will then use simple linear regression and random forest models to identify variables of importance, these variables will be noted and used later during the modeling phase. I will utilize cross validation during the modeling phase. This section will be filled out more once we are further into the class and have discussed more approaches/methods.

@@

\- Notes (Will be expanded and explained in future update):

@@

>>>>

|--------------------|----------------------------------------------------|

@@

@@

This data comes from CDC and will be sampled during analysis.

### Outcome of Interest

@@

For my analysis, I will first look at the distributions of each variable to identify if the dataset is balanced and outliers. I do not think any data cleaning will need to be done as that was completed when the data was collected from the CDC's website. Next, I will create a correlation matrix to view the correlations between each predictor and the response variable. After viewing the correlations, I will then use simple linear regression and random forest models to identify variables of importance, these variables will be noted and used later during the modeling phase. I will utilize cross validation during the modeling phase. This section will be filled out more once we are further into the class and have discussed more approaches/methods.

#### Logistic Regression

Logistic regression will be used to model the relationship between the binary outcome variable and the predictors. This method will help in understanding the influence of each predictor on the likelihood of diabetes diagnosis.

#### Random Forest

Random forest, an ensemble learning method, will be used to improve the accuracy and robustness of predictions. It will help in identifying the importance of each predictor in determining the diabetes diagnosis.

#### K-Nearest Neighbors (KNN)

KNN will be used as a non-parametric method to classify individuals based on the closest training examples in the feature space. This will provide insights into the influence of neighborhood-based predictions on diabetes diagnosis.

@@

\- Notes (Will be expanded and explained in next update):

@@

#### Model Comparisons

```{r}
knitr::include_graphics(here("results","figures","model_accuracy_comparison.png"))
```
